sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-11-02 doc/paper.Rmd
mgcv brain dump; likely not much space

>>>>

mgcv, but, yikes, do we have space:

- mgcv is capable of fitting with the SPDE (REF)
- typical smoothers don't offer MVN interpretability
- Tweedie is a big factor... must fix power 'p' to fit a GAMM.
- Barrier approaches are different
- doesn't have functionality built in for indexes/COG and uncertainty on such derived parameters
- for this class of models, we think sdmTMB has advantages, but mgcv is an immensely powerful modelling package that extends well beyond spatial/spatiotemporal data.
